Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2016-01-17 cordillera-cycle.tex
Typeset: add LaTeX hacks in header.
Typeset: add received and accepted dates.
Typeset: fix affiliations.

\documentclass[tc, manuscript]{copernicus}

\graphicspath{{figures/}}

\begin{document}

@@

\Author[1,2,3]{J.}{Seguinot}
\Author[3]{I.}{Rogozhina}
\Author[2]{A.~P.}{Stroeven}
\Author[2]{M.}{Margold}
\Author[2]{J.}{Kleman}
\runningauthor{J.~Seguinot et~al.}
\correspondence{J.~Seguinot (seguinot@vaw.baug.ethz.ch)}

@@

\affil[1]{Laboratory of Hydraulics, Hydrology and Glaciology, ETH Zürich,
          Zürich, Switzerland}
\affil[2]{Department of Physical Geography and the Bolin Centre for Climate
          Research, Stockholm University, Stockholm, Sweden}
\affil[3]{Helmholtz Centre Potsdam, GFZ German Research Centre for Geosciences,
          Potsdam, Germany}

\received{}
\pubdiscuss{}
\revised{}
\accepted{}
\published{}

\firstpage{1}
\maketitle

>>>>

\documentclass[tc, manuscript]{copernicus}
\graphicspath{{figures/}}

\begin{document}\hack{\sloppy}

@@

\Author[1,2,3]{J.}{Seguinot}
\Author[3]{I.}{Rogozhina}
\Author[2]{A.~P.}{Stroeven}
\Author[2]{M.}{Margold}
\Author[2]{J.}{Kleman}

\runningauthor{J.~Seguinot et~al.}

\correspondence{J.~Seguinot (seguinot@vaw.baug.ethz.ch)}

@@

\affil[1]{Laboratory of Hydraulics, Hydrology and Glaciology, ETH Z\"{u}rich, Z\"{u}rich, Switzerland}
\affil[2]{Department of Physical Geography and the Bolin Centre for Climate Research, Stockholm University, Stockholm, Sweden}
\affil[3]{Helmholtz Centre Potsdam, GFZ German Research Centre for Geosciences, Potsdam,~Germany}

\hack{\allowdisplaybreaks}

\received{21~June 2015}
\accepted{25~June 2015}
\published{}

\firstpage{1}

\maketitle
